\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}

\begin{enumerate}
\item Dr. Thiruvannamalai Sivasankar P [Professor (Program Head)]
  \begin{itemize}
    \item P1 - Formal Languages and Automat Theory, Sem 3, LTPE 3-0-0-3
    \item Y13 - Computational complexity Theory, Sem 1, LTPE 3-0-2-3
  \end{itemize}
\item Dr. S. Nagaraj [Associate Professor]
  \begin{itemize}
    \item P2 - Computer  Organisation And Architecture, Sem 3, LTPE 2-0-2-2
    \item P3 - It Workshop Sky/Mat Lab, Sem 7, LTPE 2-0-4-2
    \item P16 - GenAI, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. C Mahiba [Assistant Professor]
  \begin{itemize}
    \item P4 - Object Oriented Programming, Sem 3, LTPE 2-0-2-2
    \item P5 - S/W DESIGN with UML, Sem 5, LTPE 2-0-2-3
    \item P6 - Elective III:  Cryptology, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Santosh Kumar [Assistant Professor]
  \begin{itemize}
    \item P7 - Software Engineering, Sem 3, LTPE 2-0-2-2
    \item P8 - Conversstional System, Sem 5, LTPE 2-0-2-2
    \item P9 - Elective  IV:  Advanced Social, Text and Media Analytics, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Ms. Aishwarya R [Assistant Professor]
  \begin{itemize}
    \item P10 - Machine Learning, Sem 5, LTPE 2-0-2-2
    \item P11 - Usability Design Of Software Applications, Sem 7, LTPE 2-0-2-0
    \item P12 - Essence of Indian Traditional Knowledge, Sem 5, LTPE 2-0-0-2
  \end{itemize}
\item Mr. Uday Kumar Singh  [Asssistant Professor ]
  \begin{itemize}
    \item P13 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item P14 - Computational Statistics, Sem 3, LTPE 2-0-2-2
    \item P15 - Cloud Computing and Virtualization, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Shajahan B [Professor (Program Head)]
  \begin{itemize}
    \item B3 - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item U6 - Introduction To Cryptography, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Nishant Tripathi [Assistant Professor]
  \begin{itemize}
    \item B6 - Introduction to Cyber Physical Systems, Sem 3, LTPE 2-0-2-2
    \item C5 - Computer  Organisation and Architecture, Sem 3, LTPE 3-0-0-3
    \item E14A - Leadership and Negotiation Skills, Sem 5, LTPE 2-0-0-2
    \item B18A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Santhosh S [Assistant Professor (Program Head)]
  \begin{itemize}
    \item A16 - Agile Software Development, Sem 5, LTPE 3-0-0-0
    \item N21 - Computer Organization and Architecture, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Anthoni Raj [Professor]
  \begin{itemize}
    \item A5 - Infrastructure Solution on Cloud, Sem 7, LTPE 2-0-2-0
    \item A13 - Cloud Computing and Virtualization, Sem 5, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Ramesh Babu J [Associate Professor]
  \begin{itemize}
    \item A4 - Containers and Dockers, Sem 7, LTPE 2-0-2-0
    \item A15 - Communication Protocol, Sem 5, LTPE 2-0-2-0
    \item A22 - Computer  Organisation and Architecture, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Mr. Shantha Kumar [Assistant Professor]
  \begin{itemize}
    \item A2 - Software Architecture and Design, Sem 7, LTPE 3-0-0-0
    \item A12 - Software Testing, Sem 5, LTPE 1-0-2-0
    \item A23 - Software Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Mr. S. Karthikeyan [Assistant Professor]
  \begin{itemize}
    \item A3 - Software Project Management, Sem 7, LTPE 2-0-0-0
    \item A11 - Web Programming, Sem 5, LTPE 0-0-4-0
    \item A19 - Operating Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Janarthanan Sekar [Assistant Professor]
  \begin{itemize}
    \item A8 - UI/UX Design Principles, Sem 7, LTPE 2-0-2-0
    \item A24 - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item A25 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Sunanda Das [Associate Professor (Program Head)]
  \begin{itemize}
    \item W20 - Data Analytics and Machine Learning for Cyber security  Elective-2, Sem 5, LTPE 3-0-0-3
    \item R13B - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Ravikumar Sethuraman [Associate Professor]
  \begin{itemize}
    \item W1 - Cyber Risk Analysis, Sem 7, LTPE 1-0-2-0
    \item W30 - Cloud Security, Sem 3, LTPE 1-0-2-1
    \item W17 - Mobile Forensics and Security, Sem 5, LTPE 0-0-4-0
  \end{itemize}
\item Dr. R. Vijayanand [Associate Professor]
  \begin{itemize}
    \item W3 - Elective-4 Wireless Security, Sem 7, LTPE 3-0-0-0
    \item W19 - Cryptography Elective-2, Sem 5, LTPE 3-0-0-3
    \item R1A - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Harinee. S [Assistant Professor]
  \begin{itemize}
    \item W10 - Elective-5 Offensive, Defensive Cyber Security Techniques, Sem 7, LTPE 3-0-0-0
    \item W18 - Disaster Recovery, Sem 5, LTPE 1-0-2-1
    \item W31 - Elective-1 Network Defence, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Mr Vasanth Ravi [Assistant Professor]
  \begin{itemize}
    \item W4 - Elective-4 Applications of AI, Sem 7, LTPE 3-0-0-0
    \item W12 - Digital Forensics, Sem 5, LTPE 1-0-2-1
    \item W32 - Elective-1 Introduction to AI and ML, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Mr. Aniruddha Prabhu B P [Assistant Professor]
  \begin{itemize}
    \item W13 - Data Protection and Data Security, Sem 5, LTPE 1-0-2-1
    \item W25 - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
    \item W2 - Cyber security Administration, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Ms. Ambili K N [Assistant Professor]
  \begin{itemize}
    \item W11 - Elective-5 Speech recognition, Sem 7, LTPE 3-0-0-0
    \item W14 - Cyber Risk Analysis, Sem 5, LTPE 1-0-2-1
    \item W29 - Database Management Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Rajanikanta Mohanty [Associate Professor(Program Head)]
  \begin{itemize}
    \item E6 - Department Specific Elective V - geographical information systems GIS, Sem 7, LTPE 3-0-0-0
    \item E23 - Essentials of Big Data, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. A. Priyadharshini [Assistant Professor]
  \begin{itemize}
    \item E12 - Essentials of Deep Learning, Sem 5, LTPE 1-0-2-1
    \item E21 - Machine Learning, Sem 3, LTPE 2-0-2-2
    \item E25 - Advance Python Programming, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Mr. Vivek Gupta [Assistant Professor]
  \begin{itemize}
    \item E5 - Department Specific Elective IV recommender system, Sem 7, LTPE 3-0-0-0
    \item E10 - Cloud Computing and Virtualization, Sem 5, LTPE 2-0-2-2
    \item E24 - Essentials of Data Warehousing and Data Mining, Sem 3, LTPE 1-0-2-1
  \end{itemize}
\item Dr. Pajany M [Assistant Professor ]
  \begin{itemize}
    \item E11 - Scala Programming, Sem 5, LTPE 0-0-4-0
    \item E19 - Operating System, Sem 3, LTPE 2-0-2-2
    \item E34A - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. J Somasekar [Professor (Program Head)]
  \begin{itemize}
    \item C1 - Database Management Systems, Sem 3, LTPE 2-0-2-0
    \item E20 - Database Management Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. S Prakash [Assitant Professor]
  \begin{itemize}
    \item C4 - Artificial Intelligence, Sem 3, LTPE 2-0-2-0
    \item R8B - Elective -1 Application to AI, Sem 3, LTPE 3-0-0-3
    \item C6 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Mr Vaibhav Prabhakar Raibole [Assistant Professor]
  \begin{itemize}
    \item C2 - Software engineering and project management, Sem 3, LTPE 3-0-0-3
    \item B5 - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item X6 - Software Reliability, Sem 3, LTPE 3-0-0-2
  \end{itemize}
\item Dr. Manujakshi B C [Associate Professor (Program Head)]
  \begin{itemize}
    \item S3 - Computer Organisation and Architecture, Sem 3, LTPE 3-0-0-3
    \item B2 - Computer Architecture and Organization, Sem 3, LTPE 3-0-0-3
    \item U4 - Computer Organization and Architecture, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Saravana Kumar R [Professor]
  \begin{itemize}
    \item S6 - Bigdata Analytics, Sem 5, LTPE 2-0-2-2
    \item S14 - Social Medial Analytics, Sem 7, LTPE 3-0-0-3
  \end{itemize}
\item Dr. A Suresh Kumar [Professor (PHD Co ordinator)]
  \begin{itemize}
    \item S8 - CC and V, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Manikandan P [Associate Professor]
  \begin{itemize}
    \item S11 - Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item E34B - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. S Annamalai [Associate Professor]
  \begin{itemize}
    \item S10 - Data Visiualization using Tableau, Sem 5, LTPE 2-0-2-2
    \item S12 - Spark for data science, Sem 7, LTPE 2-0-2-2
  \end{itemize}
\item Dr. S Saravanakumar [Associate Professor]
  \begin{itemize}
    \item S13 - Advanced Machine Learning, Sem 7, LTPE 0-0-4-0
    \item R21C - Elective -4 - Speech Recognition, Sem 7, LTPE 3-0-0-0
  \end{itemize}
\item Dr. I Ambika [Associate Professor]
  \begin{itemize}
    \item S5 - Data Warehousing and Data Mining, Sem 3, LTPE 2-0-0-2
    \item S9 - Python for Data Science, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. John Basha [Assistant Professor]
  \begin{itemize}
    \item S16 - Bigdata Analytics on cloud, Sem 7, LTPE 2-0-2-2
    \item S7 - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
    \item E9 - BigData Analytics, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Suresh Kumar N [Assistant Professor]
  \begin{itemize}
    \item S1 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item S4 - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item E13 - Computer Vision and Image Processing, Sem 5, LTPE 1-0-2-1
  \end{itemize}
\item Mr Rajesh Pandian N [Assistant Professor]
  \begin{itemize}
    \item S2 - Oerating System, Sem 3, LTPE 2-0-2-2
    \item S13 - Advanced Machine Learning, Sem 7, LTPE 0-0-4-0
    \item E1 - Computer Vision and Image Processing, Sem 7, LTPE 1-0-2-0
  \end{itemize}
\item Dr. Sonal Sharma [Associate Professor (Program Head)]
  \begin{itemize}
    \item T1 - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item W26 - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item T30B - Data Structure Using C, Sem 1, LTPE 2-0-0-2
  \end{itemize}
\item Dr. Garima Sinha [Professor]
  \begin{itemize}
    \item T5 - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item X5 - Software Project Management, Sem 1, LTPE 3-0-0-2
  \end{itemize}
\item Dr. B. Swaminathan [Professor]
  \begin{itemize}
    \item T16 - Mobile Computing, Sem 5, LTPE 2-0-0-2
    \item T25 - Cyber Threats and Attack Vectors, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. T V Raman [Associate Professor]
  \begin{itemize}
    \item T26 - IT Governance , Risk, and information security management, Sem 7, LTPE 2-0-2-0
    \item Y5 - Agile principles, Sem 1, LTPE 3-0-0-3
    \item X4 - Agile principles, Sem 1, LTPE 3-0-0-2
  \end{itemize}
\item Dr. Rajapraveen Kumar N [Associate Professor]
  \begin{itemize}
    \item T9 - Information Security, Sem 5, LTPE 2-0-2-2
    \item T24 - Cyber security and Risk Analysis, Sem 7, LTPE 2-0-2-0
    \item T13 - Essentials of Big Data Analytics, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. V. Manikandan [Assistant Professor]
  \begin{itemize}
    \item T8 - Storage Management and Data Center, Sem 5, LTPE 2-0-0-2
    \item T20 - Advanced Android Application Development, Sem 7, LTPE 2-0-2-0
    \item T27 - Infrastructure Solution on Cloud, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Vijayanand S [Assistant Professor]
  \begin{itemize}
    \item T11 - Ethical Hacking, Sem 5, LTPE 2-0-2-2
    \item T18 - Cross Platform Application, Sem 7, LTPE 2-0-2-0
    \item T21 - Cloud Data Engineer, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Preeti Gupta [Assistant Professor]
  \begin{itemize}
    \item K3 - Smart Contracts, Sem 7, LTPE 2-0-2-0
    \item T14 - Web Programming, Sem 5, LTPE 0-0-4-0
    \item T22 - Introduction to Blockchain Technology, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Vikram Neerugatti [Associate Professor (Program Head)]
  \begin{itemize}
    \item K7 - Communication Protocol, Sem 7, LTPE 2-0-2-0
    \item Y6 - Software Project Management, Sem 1, LTPE 3-0-0-3
    \item K21A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Suresh K [Professor]
  \begin{itemize}
    \item K5 - Fog Computing, Sem 7, LTPE 2-0-2-0
    \item K18 - Internet of Things, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. M. Kumaresan [Associate Professor]
  \begin{itemize}
    \item K1 - IoT System Design, Sem 7, LTPE 2-0-2-0
    \item K17 - Communication Networks, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Panduranga Rao [Professor]
  \begin{itemize}
    \item K6 - Intellectual Property Rights, Sem 7, LTPE 2-0-0-0
    \item E26 - Domain Specific Elective I, Sem 3, LTPE 3-0-0-0
  \end{itemize}
\item Mr. Basavaraju D R [Assistant Professor]
  \begin{itemize}
    \item K9 - Microprocessor and  Microcontrollers, Sem 5, LTPE 2-0-2-2
    \item K14 - Computer Organization and Architecture, Sem 3, LTPE 3-0-0-3
    \item T3 - Computer Organisation and Architecture, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Srinivasa Rao [Assistant Professor]
  \begin{itemize}
    \item K2 - Business Intelligence for IOT, Sem 7, LTPE 2-0-2-0
    \item K10 - Data warehousing and data mining, Sem 5, LTPE 2-0-2-2
    \item Y8 - Distributed DBMS (AI+DS), Sem 3, LTPE 3-0-0-3
    \item X7 - Distributed DBMS (cse), Sem 3, LTPE 3-0-0-2
  \end{itemize}
\item Mr  Uday Prasad [Assistant Professor]
  \begin{itemize}
    \item K19 - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item K20 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item K11 - IOT Platform Design, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Ms Shobha H R [Assistant Professor]
  \begin{itemize}
    \item K12 - Web Programming, Sem 5, LTPE 0-0-4-0
    \item K15 - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item K4 - Predictive Models in IOT using Machine Learning, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. A.Vijayakumar [Associate Professor]
  \begin{itemize}
    \item K13 - Essential of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item K16 - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item W28 - Scripting for Hackers, Sem 3, LTPE 2-0-0-2
  \end{itemize}
\item Dr. Devaraj Verma C [Professor - (Progeam Head)]
  \begin{itemize}
    \item U5 - Foundation of cloud computing, Sem 3, LTPE 3-0-0-3
    \item U11 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. N Priya [Assistant Professor]
  \begin{itemize}
    \item U7 - Introduction to Blockchain Technology, Sem 3, LTPE 2-0-2-2
    \item W24 - Web Application Security, Sem 3, LTPE 1-0-4-1
    \item W7 - Penetration Testing, Sem 7, LTPE 1-0-2-0
  \end{itemize}
\item Dr. A. Rajesh [Professor (Program Head)]
  \begin{itemize}
    \item N1 - Advanced Deep Learning, Sem 7, LTPE 0-0-4-0
    \item Y2 - Knowledge Representation and Reasoning, Sem 1, LTPE 3-0-2-3
  \end{itemize}
\item Dr. N. Satheesh [Professor]
  \begin{itemize}
    \item N4 - Reinforcement Learning, Sem 7, LTPE 2-0-2-0
    \item N2 - Computer Vision, Sem 7, LTPE 1-0-2-0
  \end{itemize}
\item Dr. Janaki Kandasamy [Associate Professor]
  \begin{itemize}
    \item N5 - Deep Learning in Genomics, Sem 7, LTPE 2-0-2-0
    \item N10 - Web Programming, Sem 5, LTPE 0-0-4-0
    \item N16 - Image Processing, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Mr. Narasimhayya B E [Assistant Professor]
  \begin{itemize}
    \item N25 - Artificial Intelligence, Sem 3, LTPE 2-0-2-2
    \item N14 - Industrial AI, Sem 5, LTPE 2-0-0-2
    \item A6 - Data Modelling with NoSQL Databases, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Mrs. Sunena Rose M V [Assistant Professor]
  \begin{itemize}
    \item N12 - Natural Language Processing, Sem 5, LTPE 2-0-2-2
    \item N22 - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item M24D - Data Analytics using SQL, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Gowri Shankar J [Assistant professor]
  \begin{itemize}
    \item N23 - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item N24 - Software Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. T. Sheik Yousuf [Associate Professor]
  \begin{itemize}
    \item N3 - Recommender Systems, Sem 7, LTPE 3-0-0-0
    \item N17 - Data mining, Sem 5, LTPE 2-0-2-2
    \item E15 - Department Specific Elective II, Sem 5, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Rajasimha A Makaram [Professor ]
  \begin{itemize}
    \item T4 - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item R1D - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Mahesh TR [Associate Professor (Program Head)]
  \begin{itemize}
    \item M5A - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item M5B - Database Management Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr Deepak K Sinha [Professor + Deputy Director]
  \begin{itemize}
    \item M9A - Essentials of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item Y3 - Machine Learning, Sem 1, LTPE 3-0-2-3
  \end{itemize}
\item Dr. Kamlesh Tiwari  [HOD CSE]
  \begin{itemize}
    \item M1A - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item R11A - Essentials of Deep Learning, Sem 5, LTPE 1-0-2-1
  \end{itemize}
\item Dr. Ajay Kumar Singh [Professor (Program Head)]
  \begin{itemize}
    \item M10A - Fundamentals of Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item Y7 - Prompt Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Gowthul Alam M M [Professor]
  \begin{itemize}
    \item M18D - Data Visualization using Tableau, Sem 7, LTPE 2-0-2-0
    \item M18E - Data Visualization using Tableau, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. D Ramya Dorai [Associate Professor]
  \begin{itemize}
    \item M5C - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item R23C - Elective -5 - Environment Analysis, Sem 7, LTPE 3-0-0-0
  \end{itemize}
\item Dr. Karthick Raghunath K M [Associate Professor]
  \begin{itemize}
    \item M9B - Essentials of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item M9E - Essentials of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item T15 - Fundamental of IoS Development in Swift, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Babasaheb Satpute [Associate Professor]
  \begin{itemize}
    \item M9C - Essentials of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item M9D - Essentials of Machine Learning, Sem 5, LTPE 2-0-2-2
    \item T19 - Mobile game app development platforms, Sem 7, LTPE 2-0-2-0
    \item M25A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Giddaluri Nagendra Babu [Associate Professor]
  \begin{itemize}
    \item M19A - Essentials of Software Quality Assurance, Sem 7, LTPE 3-0-0-0
    \item M19B - Essentials of Software Quality Assurance, Sem 7, LTPE 3-0-0-0
    \item R13C - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. S Jerald Nirmal Kumar [Associate Professor]
  \begin{itemize}
    \item M6D - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
    \item M6E - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
    \item N15 - Research Methodology, Sem 5, LTPE 2-0-0-2
  \end{itemize}
\item Dr. Sowmya M S [Assistant Professor]
  \begin{itemize}
    \item M20D - Essentials of Internet of Things, Sem 7, LTPE 3-0-0-0
    \item M20E - Essentials of Internet of Things, Sem 7, LTPE 3-0-0-0
    \item M8D - Software Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Ms. Shashikala H K [Assistant Professor]
  \begin{itemize}
    \item M6A - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
    \item M6B - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
    \item M6C - Foundations of Cloud Computing, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Ms  Geetha Rani K [Assistant Professor]
  \begin{itemize}
    \item M8A - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item M8B - Software Engineering, Sem 3, LTPE 3-0-0-3
    \item M8C - Software Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Mr. Lanke Ravi Kumar [Assistant Professor]
  \begin{itemize}
    \item M21A - RestAPIs using Spring Boot Framework, Sem 7, LTPE 2-0-2-0
    \item M21B - RestAPIs using Spring Boot Framework, Sem 7, LTPE 2-0-2-0
    \item M16E - Backend Programming, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Suriya Prakash [Assistant Professor]
  \begin{itemize}
    \item M12A - Advanced Computer Networks, Sem 5, LTPE 2-0-2-2
    \item M12B - Advanced Computer Networks, Sem 5, LTPE 2-0-2-2
    \item X3 - Distributed DBMS, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Moin Hasan [Assistant Professor]
  \begin{itemize}
    \item M7A - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item M7E - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item X10 - Distributed Computing, Sem 1, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Balajee Alphonse [Assistant Professor]
  \begin{itemize}
    \item M10D - Fundamentals of Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item M10E - Fundamentals of Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item M21C - RestAPIs using Spring Boot Framework, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Ravindra Raman Cholla [Assistant Professor]
  \begin{itemize}
    \item M19C - Essentials of Software Quality Assurance, Sem 7, LTPE 3-0-0-0
    \item M19D - Essentials of Software Quality Assurance, Sem 7, LTPE 3-0-0-0
    \item M19E - Essentials of Software Quality Assurance, Sem 7, LTPE 3-0-0-0
  \end{itemize}
\item Dr. Shivkumar C [Assistant Professor]
  \begin{itemize}
    \item M17A - Data modelling with NOSQL Database, Sem 5, LTPE 2-0-2-2
    \item M17B - Data modelling with NOSQL Database, Sem 5, LTPE 2-0-2-2
    \item M17C - Data modelling with NOSQL Database, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Mr Mir Junaid Rasool [Assistant Professor]
  \begin{itemize}
    \item M23A - Frontend Framework using Angular and React, Sem 7, LTPE 2-0-2-0
    \item M23B - Frontend Framework using Angular and React, Sem 7, LTPE 2-0-2-0
    \item M23C - Frontend Framework using Angular and React, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Ms. Agashini [Assistant Professor]
  \begin{itemize}
    \item M7C - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item M7D - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item M8E - Software Engineering, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Guruvammal S. [Assistant Professor]
  \begin{itemize}
    \item M7B - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item Y12 - Data Wareshousing and Data Mining, Sem 1, LTPE 3-0-2-3
    \item N13 - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Ms. Abhisek Midya [Assistant Professor]
  \begin{itemize}
    \item M10B - Fundamentals of Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item M10C - Fundamentals of Artificial Intelligence, Sem 5, LTPE 2-0-2-2
    \item M1B - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item M25B - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Somashekhara Reddy D [Assistant Professor]
  \begin{itemize}
    \item M20A - Essentials of Internet of Things, Sem 7, LTPE 3-0-0-0
    \item M20B - Essentials of Internet of Things, Sem 7, LTPE 3-0-0-0
    \item M20C - Essentials of Internet of Things, Sem 7, LTPE 3-0-0-0
  \end{itemize}
\item Dr. Subhankar Ghosal [Assistant Professor]
  \begin{itemize}
    \item X13 - Prompt Engineering, Sem 3, LTPE 3-0-0-2
    \item M24E - Data Analytics using SQL, Sem 7, LTPE 2-0-2-0
    \item M16D - Backend Programming, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr Prasad P S [Professor]
  \begin{itemize}
    \item M12C - Advanced Computer Networks, Sem 5, LTPE 2-0-2-2
    \item M12D - Advanced Computer Networks, Sem 5, LTPE 2-0-2-2
    \item M12E - Advanced Computer Networks, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Harpreet Kaur  [Assistant Professor]
  \begin{itemize}
    \item M5E - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item M5D - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item X2 - Data Science With Python, Sem 1, LTPE 3-0-2-2
  \end{itemize}
\item Ms.  Paranjalika Das  [Assistant Professor]
  \begin{itemize}
    \item M1C - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item M1D - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item M1E - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Yogesh Kumaran [Assistant Professor]
  \begin{itemize}
    \item P17 - IT Project Management, Sem 7, LTPE 2-0-4-0
    \item U3 - Operating Systems, Sem 3, LTPE 2-0-2-2
    \item B4 - Operating Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Sukumar [Professor]
  \begin{itemize}
    \item R10D - Elective -1 - IOT, Sem 3, LTPE 3-0-0-3
    \item W21 - Leadership and Negotiation skills, Sem 5, LTPE 2-0-0-2
  \end{itemize}
\item Dr. Chandrasekar Venkatachalam [Professor (Program Head)]
  \begin{itemize}
    \item R7C - DevOps for AI, Sem 3, LTPE 0-0-4-0
    \item R1E - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Sankar K [Associate Professor]
  \begin{itemize}
    \item R13A - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
    \item R13D - Advanced Machine Learning, Sem 5, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Sugumar Ramaiyan [Associate Professor]
  \begin{itemize}
    \item R27A - Elective -2 - Blockchain, Sem 5, LTPE 3-0-0-3
    \item R12B - Computer Vision and Image Processing, Sem 5, LTPE 1-0-2-1
    \item R12D - Computer Vision and Image Processing, Sem 5, LTPE 1-0-2-1
  \end{itemize}
\item Dr. Shivam Swarup [Assistant Professor]
  \begin{itemize}
    \item R20B - Data Streaming and Analysis, Sem 7, LTPE 2-0-2-0
    \item R20C - Data Streaming and Analysis, Sem 7, LTPE 2-0-2-0
    \item R7A - DevOps for AI, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Dr. Swati Gupta [Assistant Professor]
  \begin{itemize}
    \item R3D - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item R14B - Elective -2 - Reinforcement Learning, Sem 5, LTPE 3-0-0-3
    \item R3B - Database Management Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. Rakesh Patra [Assistant Professor]
  \begin{itemize}
    \item R3A - Database Management Systems, Sem 3, LTPE 2-0-2-2
    \item R14C - Elective -2 - Reinforcement Learning, Sem 5, LTPE 3-0-0-3
    \item R3C - Database Management Systems, Sem 3, LTPE 2-0-2-2
  \end{itemize}
\item Dr. S Kanithan [Assistant Professor]
  \begin{itemize}
    \item R19B - Computer Vision and Image Processing, Sem 7, LTPE 1-0-2-0
    \item R22B - Advanced Deep Learning, Sem 7, LTPE 0-0-4-0
    \item X1 - Design And Analysis Of Algorithm, Sem 1, LTPE 3-0-2-2
  \end{itemize}
\item Dr. Renukadevi. P [Assistant Professor]
  \begin{itemize}
    \item R6D - Essentials of Data Warehousing and Data mining, Sem 3, LTPE 1-0-2-1
    \item R6C - Essentials of Data Warehousing and Data mining, Sem 3, LTPE 1-0-2-1
    \item E2 - Data Streaming and Analysis, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Archana Sasi [Assistant Professor]
  \begin{itemize}
    \item R11B - Essentials of Deep Learning, Sem 5, LTPE 1-0-2-1
    \item R11D - Essentials of Deep Learning, Sem 5, LTPE 1-0-2-1
    \item R11C - Essentials of Deep Learning, Sem 5, LTPE 1-0-2-1
  \end{itemize}
\item Dr. Senthil Kumar [Associate Professor]
  \begin{itemize}
    \item R19A - Computer Vision and Image Processing, Sem 7, LTPE 1-0-2-0
    \item R19C - Computer Vision and Image Processing, Sem 7, LTPE 1-0-2-0
    \item R22A - Advanced Deep Learning, Sem 7, LTPE 0-0-4-0
  \end{itemize}
\item Dr. Vairavel [Assistant Professor]
  \begin{itemize}
    \item R5C - Operating Systems, Sem 3, LTPE 2-0-2-0
    \item R5D - Operating Systems, Sem 3, LTPE 2-0-2-0
    \item R7B - DevOps for AI, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Mr. S Srinivas Kumar [Assistant Professor]
  \begin{itemize}
    \item R21A - Elective -4 - Speech Recognition, Sem 7, LTPE 3-0-0-0
    \item R21B - Elective -4 - Speech Recognition, Sem 7, LTPE 3-0-0-0
    \item R14D - Elective -2 - Reinforcement Learning, Sem 5, LTPE 3-0-0-3
  \end{itemize}
\item Dr. Jayashri Abhayakumar Inchal [Assistant Professor]
  \begin{itemize}
    \item R4A - Machine Learning, Sem 3, LTPE 2-0-2-2
    \item R4C - Machine Learning, Sem 3, LTPE 2-0-2-2
    \item R2A - Advanced Python Programming, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Dr. M Sayee Kumar [Associate Professor]
  \begin{itemize}
    \item R6A - Essentials of Data Warehousing and Data mining, Sem 3, LTPE 1-0-2-1
    \item R6B - Essentials of Data Warehousing and Data mining, Sem 3, LTPE 1-0-2-1
    \item R22C - Advanced Deep Learning, Sem 7, LTPE 0-0-4-0
  \end{itemize}
\item Dr. Sujeet S. Jagtap [Assistant Professor]
  \begin{itemize}
    \item R4B - Machine Learning, Sem 3, LTPE 2-0-2-2
    \item R4D - Machine Learning, Sem 3, LTPE 2-0-2-2
    \item R7D - DevOps for AI, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Mr. Divyanshu Prakash [Assistant Professor]
  \begin{itemize}
    \item R5B - Operating Systems, Sem 3, LTPE 2-0-2-0
    \item R8A - Elective -1 Application to AI, Sem 3, LTPE 3-0-0-3
    \item R8C - Elective -1 Application to AI, Sem 3, LTPE 3-0-0-3
  \end{itemize}
\item Dr. K S Arvind [Associate Professor]
  \begin{itemize}
    \item R23A - Elective -5 - Environment Analysis, Sem 7, LTPE 3-0-0-0
    \item R23B - Elective -5 - Environment Analysis, Sem 7, LTPE 3-0-0-0
    \item R2C - Advanced Python Programming, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Mr. Shahad P [Assistant Professor]
  \begin{itemize}
    \item R20A - Data Streaming and Analysis, Sem 7, LTPE 2-0-2-0
    \item R5A - Operating Systems, Sem 3, LTPE 2-0-2-0
    \item R2D - Advanced Python Programming, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Dr. Pathan Katheeja Khanam  [Assistant Professor]
  \begin{itemize}
    \item R12A - Computer Vision and Image Processing, Sem 5, LTPE 1-0-2-1
    \item R12C - Computer Vision and Image Processing, Sem 5, LTPE 1-0-2-1
    \item R2B - Advanced Python Programming, Sem 3, LTPE 0-0-4-0
  \end{itemize}
\item Dr. Manjula V. [Professor]
  \begin{itemize}
    \item W33 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item R1C - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item T17 - UI/UX Design Principles, Sem 7, LTPE 2-0-2-0
  \end{itemize}
\item Dr. B. Narmada [Assistant Professor]
  \begin{itemize}
    \item T29A - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item T29B - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item C3 - Operating system, Sem 3, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Ramesh S. [Professor]
  \begin{itemize}
    \item R1B - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item M1F - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Dr. Ebin P. M. [Assistant Professor]
  \begin{itemize}
    \item R29A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item R29B - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item R29C - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item R29D - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Ms. Puja Das [Assistant Professor]
  \begin{itemize}
    \item B14 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item N28 - Introduction To Problem Solving, Sem 1, LTPE 2-0-2-0
    \item Z2 - Introduction To Problem Solving (Mech Room-105), Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Mr. Shivashish Gaur [Assistant Professor]
  \begin{itemize}
    \item Z1 - Introduction To Problem Solving (EEE), Sem 1, LTPE 2-0-2-0
    \item P18A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item R29A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
  \end{itemize}
\item Ms. Laxmi Kumari Pathak [Assistant Professor-2]
  \begin{itemize}
    \item E39A - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item E39B - Data Structure Using C, Sem 1, LTPE 2-0-2-0
    \item T30A - Data Structure Using C, Sem 1, LTPE 2-0-0-2
    \item W34A - Data Structure Using C, Sem 1, LTPE 2-0-0-2
  \end{itemize}
\item Mr. Chokklingam Vijaya Kumar [Lab Instructor]
  \begin{itemize}
    \item E38A - Electrical and Electronics Engineering for Computational Thinking, Sem 1, LTPE 2-0-2-1
  \end{itemize}
\end{enumerate}

\section*{Course-wise Faculty List}
\begin{enumerate}
  \item Formal Languages and Automat Theory
    \begin{itemize}
      \item Dr. Thiruvannamalai Sivasankar P [Professor (Program Head)] (1-P)
    \end{itemize}
  \item Computational complexity Theory
    \begin{itemize}
      \item Dr. Thiruvannamalai Sivasankar P [Professor (Program Head)] (1-P)
    \end{itemize}
  \item Computer  Organisation And Architecture
    \begin{itemize}
      \item Dr. S. Nagaraj [Associate Professor] (1-P)
    \end{itemize}
  \item It Workshop Sky/Mat Lab
    \begin{itemize}
      \item Dr. S. Nagaraj [Associate Professor] (1-P)
    \end{itemize}
  \item GenAI
    \begin{itemize}
      \item Dr. S. Nagaraj [Associate Professor] (1-P)
    \end{itemize}
  \item Object Oriented Programming
    \begin{itemize}
      \item Dr. C Mahiba [Assistant Professor] (1-P)
    \end{itemize}
  \item S/W DESIGN with UML
    \begin{itemize}
      \item Dr. C Mahiba [Assistant Professor] (1-P)
    \end{itemize}
  \item Elective III:  Cryptology
    \begin{itemize}
      \item Dr. C Mahiba [Assistant Professor] (1-P)
    \end{itemize}
  \item Software Engineering
    \begin{itemize}
      \item Dr. Gowri Shankar J [Assistant professor] (1-N)
      \item Dr. Rajasimha A Makaram [Professor ] (1-M)
      \item Dr. Santosh Kumar [Assistant Professor] (1-P)
      \item Dr. Sowmya M S [Assistant Professor] (1-M)
      \item Dr. Suresh Kumar N [Assistant Professor] (1-S)
      \item Mr  Uday Prasad [Assistant Professor] (1-K)
      \item Mr Vaibhav Prabhakar Raibole [Assistant Professor] (1-C)
      \item Mr. Shantha Kumar [Assistant Professor] (1-A)
      \item Ms  Geetha Rani K [Assistant Professor] (1-M)
      \item Ms. Agashini [Assistant Professor] (1-M)
    \end{itemize}
  \item Conversstional System
    \begin{itemize}
      \item Dr. Santosh Kumar [Assistant Professor] (1-P)
    \end{itemize}
  \item Elective  IV:  Advanced Social, Text and Media Analytics
    \begin{itemize}
      \item Dr. Santosh Kumar [Assistant Professor] (1-P)
    \end{itemize}
  \item Machine Learning
    \begin{itemize}
      \item Dr Deepak K Sinha [Professor + Deputy Director] (1-M)
      \item Dr. A. Priyadharshini [Assistant Professor] (1-E)
      \item Dr. Jayashri Abhayakumar Inchal [Assistant Professor] (1-R)
      \item Dr. Sujeet S. Jagtap [Assistant Professor] (1-R)
      \item Ms. Aishwarya R [Assistant Professor] (1-P)
    \end{itemize}
  \item Usability Design Of Software Applications
    \begin{itemize}
      \item Ms. Aishwarya R [Assistant Professor] (1-P)
    \end{itemize}
  \item Essence of Indian Traditional Knowledge
    \begin{itemize}
      \item Ms. Aishwarya R [Assistant Professor] (1-P)
    \end{itemize}
  \item Introduction To Problem Solving
    \begin{itemize}
      \item Dr. B. Narmada [Assistant Professor] (1-T)
      \item Dr. Chandrasekar Venkatachalam [Professor (Program Head)] (1-R)
      \item Dr. Devaraj Verma C [Professor - (Progeam Head)] (1-U)
      \item Dr. Janarthanan Sekar [Assistant Professor] (1-A)
      \item Dr. Kamlesh Tiwari  [HOD CSE] (1-M)
      \item Dr. Manikandan P [Associate Professor] (1-S)
      \item Dr. Manjula V. [Professor] (1-A)
      \item Dr. Pajany M [Assistant Professor ] (1-E)
      \item Dr. R. Vijayanand [Associate Professor] (1-W)
      \item Dr. Rajasimha A Makaram [Professor ] (1-M)
      \item Dr. Ramesh S. [Professor] (1-S)
      \item Dr. S Prakash [Assitant Professor] (1-C)
      \item Dr. Suresh Kumar N [Assistant Professor] (1-S)
      \item Mr  Uday Prasad [Assistant Professor] (1-K)
      \item Mr. Uday Kumar Singh  [Asssistant Professor ] (1-P)
      \item Ms.  Paranjalika Das  [Assistant Professor] (1-M)
      \item Ms. Abhisek Midya [Assistant Professor] (1-M)
      \item Ms. Puja Das [Assistant Professor] (1-B)
    \end{itemize}
  \item Computational Statistics
    \begin{itemize}
      \item Mr. Uday Kumar Singh  [Asssistant Professor ] (1-P)
    \end{itemize}
  \item Cloud Computing and Virtualization
    \begin{itemize}
      \item Dr. Anthoni Raj [Professor] (1-A)
      \item Mr. Uday Kumar Singh  [Asssistant Professor ] (1-P)
      \item Mr. Vivek Gupta [Assistant Professor] (1-E)
    \end{itemize}
  \item Database Management Systems
    \begin{itemize}
      \item Dr. D Ramya Dorai [Associate Professor] (1-M)
      \item Dr. Garima Sinha [Professor] (1-T)
      \item Dr. Harpreet Kaur  [Assistant Professor] (1-M)
      \item Dr. J Somasekar [Professor (Program Head)] (1-C)
      \item Dr. Janarthanan Sekar [Assistant Professor] (1-A)
      \item Dr. Mahesh TR [Associate Professor (Program Head)] (1-M)
      \item Dr. Rakesh Patra [Assistant Professor] (1-R)
      \item Dr. Shajahan B [Professor (Program Head)] (1-B)
      \item Dr. Swati Gupta [Assistant Professor] (1-R)
      \item Mrs. Sunena Rose M V [Assistant Professor] (1-N)
      \item Ms Shobha H R [Assistant Professor] (1-K)
      \item Ms. Ambili K N [Assistant Professor] (1-W)
    \end{itemize}
  \item Introduction To Cryptography
    \begin{itemize}
      \item Dr. Shajahan B [Professor (Program Head)] (1-B)
    \end{itemize}
  \item Introduction to Cyber Physical Systems
    \begin{itemize}
      \item Dr. Nishant Tripathi [Assistant Professor] (1-B)
    \end{itemize}
  \item Computer  Organisation and Architecture
    \begin{itemize}
      \item Dr. Nishant Tripathi [Assistant Professor] (1-B)
      \item Dr. Ramesh Babu J [Associate Professor] (1-A)
    \end{itemize}
  \item Leadership and Negotiation Skills
    \begin{itemize}
      \item Dr. Nishant Tripathi [Assistant Professor] (1-B)
    \end{itemize}
  \item Data Structure Using C
    \begin{itemize}
      \item Dr. Babasaheb Satpute [Associate Professor] (1-M)
      \item Dr. Ebin P. M. [Assistant Professor] (1-R)
      \item Dr. Nishant Tripathi [Assistant Professor] (1-B)
      \item Dr. Sonal Sharma [Associate Professor (Program Head)] (1-T)
      \item Dr. Vikram Neerugatti [Associate Professor (Program Head)] (1-K)
      \item Mr. Shivashish Gaur [Assistant Professor] (1-U)
      \item Ms. Abhisek Midya [Assistant Professor] (1-M)
      \item Ms. Laxmi Kumari Pathak [Assistant Professor-2] (1-R)
    \end{itemize}
  \item Agile Software Development
    \begin{itemize}
      \item Dr. Santhosh S [Assistant Professor (Program Head)] (1-A)
    \end{itemize}
  \item Computer Organization and Architecture
    \begin{itemize}
      \item Dr. Manujakshi B C [Associate Professor (Program Head)] (1-S)
      \item Dr. Santhosh S [Assistant Professor (Program Head)] (1-A)
      \item Mr. Basavaraju D R [Assistant Professor] (1-K)
    \end{itemize}
  \item Infrastructure Solution on Cloud
    \begin{itemize}
      \item Dr. Anthoni Raj [Professor] (1-A)
      \item Dr. V. Manikandan [Assistant Professor] (1-T)
    \end{itemize}
  \item Containers and Dockers
    \begin{itemize}
      \item Dr. Ramesh Babu J [Associate Professor] (1-A)
    \end{itemize}
  \item Communication Protocol
    \begin{itemize}
      \item Dr. Ramesh Babu J [Associate Professor] (1-A)
      \item Dr. Vikram Neerugatti [Associate Professor (Program Head)] (1-K)
    \end{itemize}
  \item Software Architecture and Design
    \begin{itemize}
      \item Mr. Shantha Kumar [Assistant Professor] (1-A)
    \end{itemize}
  \item Software Testing
    \begin{itemize}
      \item Mr. Shantha Kumar [Assistant Professor] (1-A)
    \end{itemize}
  \item Software Project Management
    \begin{itemize}
      \item Dr. Garima Sinha [Professor] (1-T)
      \item Dr. Vikram Neerugatti [Associate Professor (Program Head)] (1-K)
      \item Mr. S. Karthikeyan [Assistant Professor] (1-A)
    \end{itemize}
  \item Web Programming
    \begin{itemize}
      \item Dr. Janaki Kandasamy [Associate Professor] (1-N)
      \item Dr. Preeti Gupta [Assistant Professor] (1-T)
      \item Mr. S. Karthikeyan [Assistant Professor] (1-A)
      \item Ms Shobha H R [Assistant Professor] (1-K)
    \end{itemize}
  \item Operating Systems
    \begin{itemize}
      \item Dr. A.Vijayakumar [Associate Professor] (1-K)
      \item Dr. Gowri Shankar J [Assistant professor] (1-N)
      \item Dr. Guruvammal S. [Assistant Professor] (1-M)
      \item Dr. Moin Hasan [Assistant Professor] (1-M)
      \item Dr. Sonal Sharma [Associate Professor (Program Head)] (1-T)
      \item Dr. Vairavel [Assistant Professor] (1-R)
      \item Dr. Yogesh Kumaran [Assistant Professor] (1-M)
      \item Mr. Divyanshu Prakash [Assistant Professor] (1-R)
      \item Mr. S. Karthikeyan [Assistant Professor] (1-A)
      \item Mr. Shahad P [Assistant Professor] (1-R)
      \item Ms. Agashini [Assistant Professor] (1-M)
    \end{itemize}
  \item UI/UX Design Principles
    \begin{itemize}
      \item Dr. Janarthanan Sekar [Assistant Professor] (1-A)
      \item Dr. Manjula V. [Professor] (1-A)
    \end{itemize}
  \item Data Analytics and Machine Learning for Cyber security  Elective-2
    \begin{itemize}
      \item Dr. Sunanda Das [Associate Professor (Program Head)] (1-W)
    \end{itemize}
  \item Advanced Machine Learning
    \begin{itemize}
      \item Dr. Giddaluri Nagendra Babu [Associate Professor] (1-M)
      \item Dr. Guruvammal S. [Assistant Professor] (1-M)
      \item Dr. John Basha [Assistant Professor] (1-S)
      \item Dr. S Saravanakumar [Associate Professor] (1-S)
      \item Dr. Sankar K [Associate Professor] (1-R)
      \item Dr. Sunanda Das [Associate Professor (Program Head)] (1-W)
      \item Mr Rajesh Pandian N [Assistant Professor] (1-S)
    \end{itemize}
  \item Cyber Risk Analysis
    \begin{itemize}
      \item Dr. Ravikumar Sethuraman [Associate Professor] (1-W)
      \item Ms. Ambili K N [Assistant Professor] (1-W)
    \end{itemize}
  \item Cloud Security
    \begin{itemize}
      \item Dr. Ravikumar Sethuraman [Associate Professor] (1-W)
    \end{itemize}
  \item Mobile Forensics and Security
    \begin{itemize}
      \item Dr. Ravikumar Sethuraman [Associate Professor] (1-W)
    \end{itemize}
  \item Elective-4 Wireless Security
    \begin{itemize}
      \item Dr. R. Vijayanand [Associate Professor] (1-W)
    \end{itemize}
  \item Cryptography Elective-2
    \begin{itemize}
      \item Dr. R. Vijayanand [Associate Professor] (1-W)
    \end{itemize}
  \item Elective-5 Offensive, Defensive Cyber Security Techniques
    \begin{itemize}
      \item Dr. Harinee. S [Assistant Professor] (1-W)
    \end{itemize}
  \item Disaster Recovery
    \begin{itemize}
      \item Dr. Harinee. S [Assistant Professor] (1-W)
    \end{itemize}
  \item Elective-1 Network Defence
    \begin{itemize}
      \item Dr. Harinee. S [Assistant Professor] (1-W)
    \end{itemize}
  \item Elective-4 Applications of AI
    \begin{itemize}
      \item Mr Vasanth Ravi [Assistant Professor] (1-W)
    \end{itemize}
  \item Digital Forensics
    \begin{itemize}
      \item Mr Vasanth Ravi [Assistant Professor] (1-W)
    \end{itemize}
  \item Elective-1 Introduction to AI and ML
    \begin{itemize}
      \item Mr Vasanth Ravi [Assistant Professor] (1-W)
    \end{itemize}
  \item Data Protection and Data Security
    \begin{itemize}
      \item Mr. Aniruddha Prabhu B P [Assistant Professor] (1-W)
    \end{itemize}
  \item Foundations of Cloud Computing
    \begin{itemize}
      \item Dr. S Jerald Nirmal Kumar [Associate Professor] (1-M)
      \item Mr. Aniruddha Prabhu B P [Assistant Professor] (1-W)
      \item Ms. Shashikala H K [Assistant Professor] (1-M)
    \end{itemize}
  \item Cyber security Administration
    \begin{itemize}
      \item Mr. Aniruddha Prabhu B P [Assistant Professor] (1-W)
    \end{itemize}
  \item Elective-5 Speech recognition
    \begin{itemize}
      \item Ms. Ambili K N [Assistant Professor] (1-W)
    \end{itemize}
  \item Department Specific Elective V - geographical information systems GIS
    \begin{itemize}
      \item Dr. Rajanikanta Mohanty [Associate Professor(Program Head)] (1-E)
    \end{itemize}
  \item Essentials of Big Data
    \begin{itemize}
      \item Dr. Rajanikanta Mohanty [Associate Professor(Program Head)] (1-E)
    \end{itemize}
  \item Essentials of Deep Learning
    \begin{itemize}
      \item Dr. A. Priyadharshini [Assistant Professor] (1-E)
      \item Dr. Archana Sasi [Assistant Professor] (1-R)
      \item Dr. Kamlesh Tiwari  [HOD CSE] (1-M)
    \end{itemize}
  \item Advance Python Programming
    \begin{itemize}
      \item Dr. A. Priyadharshini [Assistant Professor] (1-E)
    \end{itemize}
  \item Department Specific Elective IV recommender system
    \begin{itemize}
      \item Mr. Vivek Gupta [Assistant Professor] (1-E)
    \end{itemize}
  \item Essentials of Data Warehousing and Data Mining
    \begin{itemize}
      \item Mr. Vivek Gupta [Assistant Professor] (1-E)
    \end{itemize}
  \item Scala Programming
    \begin{itemize}
      \item Dr. Pajany M [Assistant Professor ] (1-E)
    \end{itemize}
  \item Operating System
    \begin{itemize}
      \item Dr. Pajany M [Assistant Professor ] (1-E)
    \end{itemize}
  \item Artificial Intelligence
    \begin{itemize}
      \item Dr. Manikandan P [Associate Professor] (1-S)
      \item Dr. S Prakash [Assitant Professor] (1-C)
      \item Mr. Narasimhayya B E [Assistant Professor] (1-N)
    \end{itemize}
  \item Elective -1 Application to AI
    \begin{itemize}
      \item Dr. S Prakash [Assitant Professor] (1-C)
      \item Mr. Divyanshu Prakash [Assistant Professor] (1-R)
    \end{itemize}
  \item Software engineering and project management
    \begin{itemize}
      \item Mr Vaibhav Prabhakar Raibole [Assistant Professor] (1-C)
    \end{itemize}
  \item Software Reliability
    \begin{itemize}
      \item Mr Vaibhav Prabhakar Raibole [Assistant Professor] (1-C)
    \end{itemize}
  \item Computer Organisation and Architecture
    \begin{itemize}
      \item Dr. Manujakshi B C [Associate Professor (Program Head)] (1-S)
      \item Mr. Basavaraju D R [Assistant Professor] (1-K)
    \end{itemize}
  \item Computer Architecture and Organization
    \begin{itemize}
      \item Dr. Manujakshi B C [Associate Professor (Program Head)] (1-S)
    \end{itemize}
  \item Bigdata Analytics
    \begin{itemize}
      \item Dr. Saravana Kumar R [Professor] (1-S)
    \end{itemize}
  \item Social Medial Analytics
    \begin{itemize}
      \item Dr. Saravana Kumar R [Professor] (1-S)
    \end{itemize}
  \item CC and V
    \begin{itemize}
      \item Dr. A Suresh Kumar [Professor (PHD Co ordinator)] (1-S)
    \end{itemize}
  \item Data Visiualization using Tableau
    \begin{itemize}
      \item Dr. S Annamalai [Associate Professor] (1-S)
    \end{itemize}
  \item Spark for data science
    \begin{itemize}
      \item Dr. S Annamalai [Associate Professor] (1-S)
    \end{itemize}
  \item Elective -4 - Speech Recognition
    \begin{itemize}
      \item Dr. S Saravanakumar [Associate Professor] (1-S)
      \item Mr. S Srinivas Kumar [Assistant Professor] (1-R)
    \end{itemize}
  \item Data Warehousing and Data Mining
    \begin{itemize}
      \item Dr. I Ambika [Associate Professor] (1-S)
    \end{itemize}
  \item Python for Data Science
    \begin{itemize}
      \item Dr. I Ambika [Associate Professor] (1-S)
    \end{itemize}
  \item Bigdata Analytics on cloud
    \begin{itemize}
      \item Dr. John Basha [Assistant Professor] (1-S)
    \end{itemize}
  \item BigData Analytics
    \begin{itemize}
      \item Dr. John Basha [Assistant Professor] (1-S)
    \end{itemize}
  \item Computer Vision and Image Processing
    \begin{itemize}
      \item Dr. Pathan Katheeja Khanam  [Assistant Professor] (1-R)
      \item Dr. S Kanithan [Assistant Professor] (1-R)
      \item Dr. Senthil Kumar [Associate Professor] (1-R)
      \item Dr. Sugumar Ramaiyan [Associate Professor] (1-R)
      \item Dr. Suresh Kumar N [Assistant Professor] (1-S)
      \item Mr Rajesh Pandian N [Assistant Professor] (1-S)
    \end{itemize}
  \item Oerating System
    \begin{itemize}
      \item Mr Rajesh Pandian N [Assistant Professor] (1-S)
    \end{itemize}
  \item Mobile Computing
    \begin{itemize}
      \item Dr. B. Swaminathan [Professor] (1-T)
    \end{itemize}
  \item Cyber Threats and Attack Vectors
    \begin{itemize}
      \item Dr. B. Swaminathan [Professor] (1-T)
    \end{itemize}
  \item IT Governance , Risk, and information security management
    \begin{itemize}
      \item Dr. T V Raman [Associate Professor] (1-T)
    \end{itemize}
  \item Agile principles
    \begin{itemize}
      \item Dr. T V Raman [Associate Professor] (1-T)
    \end{itemize}
  \item Information Security
    \begin{itemize}
      \item Dr. Rajapraveen Kumar N [Associate Professor] (1-T)
    \end{itemize}
  \item Cyber security and Risk Analysis
    \begin{itemize}
      \item Dr. Rajapraveen Kumar N [Associate Professor] (1-T)
    \end{itemize}
  \item Essentials of Big Data Analytics
    \begin{itemize}
      \item Dr. Rajapraveen Kumar N [Associate Professor] (1-T)
    \end{itemize}
  \item Storage Management and Data Center
    \begin{itemize}
      \item Dr. V. Manikandan [Assistant Professor] (1-T)
    \end{itemize}
  \item Advanced Android Application Development
    \begin{itemize}
      \item Dr. V. Manikandan [Assistant Professor] (1-T)
    \end{itemize}
  \item Ethical Hacking
    \begin{itemize}
      \item Dr. Vijayanand S [Assistant Professor] (1-T)
    \end{itemize}
  \item Cross Platform Application
    \begin{itemize}
      \item Dr. Vijayanand S [Assistant Professor] (1-T)
    \end{itemize}
  \item Cloud Data Engineer
    \begin{itemize}
      \item Dr. Vijayanand S [Assistant Professor] (1-T)
    \end{itemize}
  \item Smart Contracts
    \begin{itemize}
      \item Dr. Preeti Gupta [Assistant Professor] (1-T)
    \end{itemize}
  \item Introduction to Blockchain Technology
    \begin{itemize}
      \item Dr. N Priya [Assistant Professor] (1-U)
      \item Dr. Preeti Gupta [Assistant Professor] (1-T)
    \end{itemize}
  \item Fog Computing
    \begin{itemize}
      \item Dr. Suresh K [Professor] (1-K)
    \end{itemize}
  \item Internet of Things
    \begin{itemize}
      \item Dr. Suresh K [Professor] (1-K)
    \end{itemize}
  \item IoT System Design
    \begin{itemize}
      \item Dr. M. Kumaresan [Associate Professor] (1-K)
    \end{itemize}
  \item Communication Networks
    \begin{itemize}
      \item Dr. M. Kumaresan [Associate Professor] (1-K)
    \end{itemize}
  \item Intellectual Property Rights
    \begin{itemize}
      \item Dr. Panduranga Rao [Professor] (1-K)
    \end{itemize}
  \item Domain Specific Elective I
    \begin{itemize}
      \item Dr. Panduranga Rao [Professor] (1-K)
    \end{itemize}
  \item Microprocessor and  Microcontrollers
    \begin{itemize}
      \item Mr. Basavaraju D R [Assistant Professor] (1-K)
    \end{itemize}
  \item Business Intelligence for IOT
    \begin{itemize}
      \item Dr. Srinivasa Rao [Assistant Professor] (1-K)
    \end{itemize}
  \item Data warehousing and data mining
    \begin{itemize}
      \item Dr. Srinivasa Rao [Assistant Professor] (1-K)
    \end{itemize}
  \item Distributed DBMS (AI+DS)
    \begin{itemize}
      \item Dr. Srinivasa Rao [Assistant Professor] (1-K)
    \end{itemize}
  \item Distributed DBMS (cse)
    \begin{itemize}
      \item Dr. Srinivasa Rao [Assistant Professor] (1-K)
    \end{itemize}
  \item IOT Platform Design
    \begin{itemize}
      \item Mr  Uday Prasad [Assistant Professor] (1-K)
    \end{itemize}
  \item Predictive Models in IOT using Machine Learning
    \begin{itemize}
      \item Ms Shobha H R [Assistant Professor] (1-K)
    \end{itemize}
  \item Essential of Machine Learning
    \begin{itemize}
      \item Dr. A.Vijayakumar [Associate Professor] (1-K)
    \end{itemize}
  \item Scripting for Hackers
    \begin{itemize}
      \item Dr. A.Vijayakumar [Associate Professor] (1-K)
    \end{itemize}
  \item Foundation of cloud computing
    \begin{itemize}
      \item Dr. Devaraj Verma C [Professor - (Progeam Head)] (1-U)
    \end{itemize}
  \item Web Application Security
    \begin{itemize}
      \item Dr. N Priya [Assistant Professor] (1-U)
    \end{itemize}
  \item Penetration Testing
    \begin{itemize}
      \item Dr. N Priya [Assistant Professor] (1-U)
    \end{itemize}
  \item Advanced Deep Learning
    \begin{itemize}
      \item Dr. A. Rajesh [Professor (Program Head)] (1-N)
      \item Dr. M Sayee Kumar [Associate Professor] (1-R)
      \item Dr. S Kanithan [Assistant Professor] (1-R)
      \item Dr. Senthil Kumar [Associate Professor] (1-R)
    \end{itemize}
  \item Knowledge Representation and Reasoning
    \begin{itemize}
      \item Dr. A. Rajesh [Professor (Program Head)] (1-N)
    \end{itemize}
  \item Reinforcement Learning
    \begin{itemize}
      \item Dr. N. Satheesh [Professor] (1-N)
    \end{itemize}
  \item Computer Vision
    \begin{itemize}
      \item Dr. N. Satheesh [Professor] (1-N)
    \end{itemize}
  \item Deep Learning in Genomics
    \begin{itemize}
      \item Dr. Janaki Kandasamy [Associate Professor] (1-N)
    \end{itemize}
  \item Image Processing
    \begin{itemize}
      \item Dr. Janaki Kandasamy [Associate Professor] (1-N)
    \end{itemize}
  \item Industrial AI
    \begin{itemize}
      \item Mr. Narasimhayya B E [Assistant Professor] (1-N)
    \end{itemize}
  \item Data Modelling with NoSQL Databases
    \begin{itemize}
      \item Mr. Narasimhayya B E [Assistant Professor] (1-N)
    \end{itemize}
  \item Natural Language Processing
    \begin{itemize}
      \item Mrs. Sunena Rose M V [Assistant Professor] (1-N)
    \end{itemize}
  \item Data Analytics using SQL
    \begin{itemize}
      \item Dr. Subhankar Ghosal [Assistant Professor] (1-M)
      \item Mrs. Sunena Rose M V [Assistant Professor] (1-N)
    \end{itemize}
  \item Recommender Systems
    \begin{itemize}
      \item Dr. T. Sheik Yousuf [Associate Professor] (1-N)
    \end{itemize}
  \item Data mining
    \begin{itemize}
      \item Dr. T. Sheik Yousuf [Associate Professor] (1-N)
    \end{itemize}
  \item Department Specific Elective II
    \begin{itemize}
      \item Dr. T. Sheik Yousuf [Associate Professor] (1-N)
    \end{itemize}
  \item Essentials of Machine Learning
    \begin{itemize}
      \item Dr Deepak K Sinha [Professor + Deputy Director] (1-M)
      \item Dr. Babasaheb Satpute [Associate Professor] (1-M)
      \item Dr. Karthick Raghunath K M [Associate Professor] (1-M)
    \end{itemize}
  \item Fundamentals of Artificial Intelligence
    \begin{itemize}
      \item Dr. Ajay Kumar Singh [Professor (Program Head)] (1-M)
      \item Dr. Balajee Alphonse [Assistant Professor] (1-M)
      \item Ms. Abhisek Midya [Assistant Professor] (1-M)
    \end{itemize}
  \item Prompt Engineering
    \begin{itemize}
      \item Dr. Ajay Kumar Singh [Professor (Program Head)] (1-M)
      \item Dr. Subhankar Ghosal [Assistant Professor] (1-M)
    \end{itemize}
  \item Data Visualization using Tableau
    \begin{itemize}
      \item Dr. Gowthul Alam M M [Professor] (1-M)
    \end{itemize}
  \item Elective -5 - Environment Analysis
    \begin{itemize}
      \item Dr. D Ramya Dorai [Associate Professor] (1-M)
      \item Dr. K S Arvind [Associate Professor] (1-R)
    \end{itemize}
  \item Fundamental of IoS Development in Swift
    \begin{itemize}
      \item Dr. Karthick Raghunath K M [Associate Professor] (1-M)
    \end{itemize}
  \item Mobile game app development platforms
    \begin{itemize}
      \item Dr. Babasaheb Satpute [Associate Professor] (1-M)
    \end{itemize}
  \item Essentials of Software Quality Assurance
    \begin{itemize}
      \item Dr. Giddaluri Nagendra Babu [Associate Professor] (1-M)
      \item Dr. Ravindra Raman Cholla [Assistant Professor] (1-M)
    \end{itemize}
  \item Research Methodology
    \begin{itemize}
      \item Dr. S Jerald Nirmal Kumar [Associate Professor] (1-M)
    \end{itemize}
  \item Essentials of Internet of Things
    \begin{itemize}
      \item Dr. Somashekhara Reddy D [Assistant Professor] (1-M)
      \item Dr. Sowmya M S [Assistant Professor] (1-M)
    \end{itemize}
  \item RestAPIs using Spring Boot Framework
    \begin{itemize}
      \item Dr. Balajee Alphonse [Assistant Professor] (1-M)
      \item Mr. Lanke Ravi Kumar [Assistant Professor] (1-M)
    \end{itemize}
  \item Backend Programming
    \begin{itemize}
      \item Dr. Subhankar Ghosal [Assistant Professor] (1-M)
      \item Mr. Lanke Ravi Kumar [Assistant Professor] (1-M)
    \end{itemize}
  \item Advanced Computer Networks
    \begin{itemize}
      \item Dr Prasad P S [Professor] (1-M)
      \item Dr. Suriya Prakash [Assistant Professor] (1-M)
    \end{itemize}
  \item Distributed DBMS
    \begin{itemize}
      \item Dr. Suriya Prakash [Assistant Professor] (1-M)
    \end{itemize}
  \item Distributed Computing
    \begin{itemize}
      \item Dr. Moin Hasan [Assistant Professor] (1-M)
    \end{itemize}
  \item Data modelling with NOSQL Database
    \begin{itemize}
      \item Dr. Shivkumar C [Assistant Professor] (1-M)
    \end{itemize}
  \item Frontend Framework using Angular and React
    \begin{itemize}
      \item Mr Mir Junaid Rasool [Assistant Professor] (1-M)
    \end{itemize}
  \item Data Wareshousing and Data Mining
    \begin{itemize}
      \item Dr. Guruvammal S. [Assistant Professor] (1-M)
    \end{itemize}
  \item Data Science With Python
    \begin{itemize}
      \item Dr. Harpreet Kaur  [Assistant Professor] (1-M)
    \end{itemize}
  \item IT Project Management
    \begin{itemize}
      \item Dr. Yogesh Kumaran [Assistant Professor] (1-M)
    \end{itemize}
  \item Elective -1 - IOT
    \begin{itemize}
      \item Dr. Sukumar [Professor] (1-M)
    \end{itemize}
  \item Leadership and Negotiation skills
    \begin{itemize}
      \item Dr. Sukumar [Professor] (1-M)
    \end{itemize}
  \item DevOps for AI
    \begin{itemize}
      \item Dr. Chandrasekar Venkatachalam [Professor (Program Head)] (1-R)
      \item Dr. Shivam Swarup [Assistant Professor] (1-R)
      \item Dr. Sujeet S. Jagtap [Assistant Professor] (1-R)
      \item Dr. Vairavel [Assistant Professor] (1-R)
    \end{itemize}
  \item Elective -2 - Blockchain
    \begin{itemize}
      \item Dr. Sugumar Ramaiyan [Associate Professor] (1-R)
    \end{itemize}
  \item Data Streaming and Analysis
    \begin{itemize}
      \item Dr. Renukadevi. P [Assistant Professor] (1-R)
      \item Dr. Shivam Swarup [Assistant Professor] (1-R)
      \item Mr. Shahad P [Assistant Professor] (1-R)
    \end{itemize}
  \item Elective -2 - Reinforcement Learning
    \begin{itemize}
      \item Dr. Rakesh Patra [Assistant Professor] (1-R)
      \item Dr. Swati Gupta [Assistant Professor] (1-R)
      \item Mr. S Srinivas Kumar [Assistant Professor] (1-R)
    \end{itemize}
  \item Design And Analysis Of Algorithm
    \begin{itemize}
      \item Dr. S Kanithan [Assistant Professor] (1-R)
    \end{itemize}
  \item Essentials of Data Warehousing and Data mining
    \begin{itemize}
      \item Dr. M Sayee Kumar [Associate Professor] (1-R)
      \item Dr. Renukadevi. P [Assistant Professor] (1-R)
    \end{itemize}
  \item Advanced Python Programming
    \begin{itemize}
      \item Dr. Jayashri Abhayakumar Inchal [Assistant Professor] (1-R)
      \item Dr. K S Arvind [Associate Professor] (1-R)
      \item Dr. Pathan Katheeja Khanam  [Assistant Professor] (1-R)
      \item Mr. Shahad P [Assistant Professor] (1-R)
    \end{itemize}
  \item Operating system
    \begin{itemize}
      \item Dr. B. Narmada [Assistant Professor] (1-T)
    \end{itemize}
  \item Introduction To Problem Solving (Mech Room-105)
    \begin{itemize}
      \item Ms. Puja Das [Assistant Professor] (1-B)
    \end{itemize}
  \item Introduction To Problem Solving (EEE)
    \begin{itemize}
      \item Mr. Shivashish Gaur [Assistant Professor] (1-U)
    \end{itemize}
  \item Electrical and Electronics Engineering for Computational Thinking
    \begin{itemize}
      \item Mr. Chokklingam Vijaya Kumar [Lab Instructor] (1-S)
    \end{itemize}
\end{enumerate}
\end{document}
